---
title: "BayesianInference_1"
author: "glg"
date: "September 26, 2016"
output: html_document
---

### RU 486 data 
4 pregnancies out of 20 from a morning after pill treatment( 16 pregnancies from the control)
if treatment and control are equally effective - then probability that the pregnancy comes from the treatment group is p = 0.5

### 9 models - any between 0 and 1

chances the pregnancy comes from the treatment group is 
10%, 20%... 90%
if p = 20% - then 1 to 4 in the treatment group.
likelihood
calculate P(data | model) for each model considered
P(k = 4|n=20,p)     p is 10% to 90%

```{r}

p <- seq(from = 0.1, to = 0.9, by =0.1)
prior <- c(rep(0.06, 4), 0.52, rep(0.06, 4))
likelihood <- dbinom(4, size = 20, prob = p)
plot(likelihood)
plot(prior)

numerator <- prior * likelihood
denominator <- sum(numerator)
posterior <- numerator / denominator
sum(posterior)  #1  - hence checks out.
plot(posterior)

```

```{r}
#add more data - this time 3 out of 20
newLikelihood <- dbinom(30,size=200, prob=p)
newPrior <- posterior
newPosterior <- newPrior * newLikelihood / sum(newPrior * newLikelihood)
barplot(newPosterior)


par(mfrow=c(1,2))
barplot(posterior, main="First round")
barplot(newPosterior, main = "second round")
```

```{r}


```



